worldmap

### 2024-05-23 analysis/figures/visualization.Rmd
Attempt at the hexbin

>>>>

Hexbin map
```{r}
coast <- rnaturalearth::ne_coastline(scale = "small", returnclass = "sf")

basemap <- ggplot(data = coast) + geom_sf(color = "grey") + 
  ggthemes::theme_map() #+
  #coord_sf(crs = 3857)  #+
  #ggthemes::theme_map()

#xlim=c(-180,180), ylim=c(-57, 90), 
bird_hexmap <- basemap +
  geom_hex(data = study_data %>% select(rarefyID, rarefyID_x, rarefyID_y, taxa) %>% 
             distinct() %>%
             filter(taxa == "Birds"),
             aes(x = rarefyID_x, y = rarefyID_y), color = "grey",# bins = 50, color = my_pal[2]) 
                 bins = 35) +
  scale_fill_gradient2()
             scale_fill_gradient(low = "#bbe9ff", high = "#086788")

mammal_hexmap <- basemap +
  geom_hex(data = study_data %>% select(rarefyID, rarefyID_x, rarefyID_y, taxa) %>% 
             distinct() %>%
             filter(taxa == "Mammals"),
             aes(x = rarefyID_x, y = rarefyID_y), color = "grey",# bins = 50, color = my_pal[2]) 
                 bins = 35) +
  scale_fill_gradient2()
```
